---
title: "amaramtiazy"
author: "luka"
date: "2025-02-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readr)
clean_data <- read_csv("C:/Users/USER/Downloads/clean_data.csv")
data<-clean_data
```


```{r}
# Transfer required columns to new dataframe
new_data <- data[, c("Name","Country", "Series", "Animation", "Western", "Adventure", "Comedy", "Family", "Fantasy", "Mystery", "Action", "Romance", "Drama", "SciFi", "ShortFilm", "Crime", "Musical", "Korean", "Thriller", "Anime", "Music")]

# Display new dataframe
print(new_data)


```

K-Modes

```{r}
# Load required libraries
library(klaR)
library(dplyr)
library(stringr)
library(readr)

# Extract columns excluding "Country" and "Name"
features <- new_data[, !names(new_data) %in% c("Country", "Name")]

# Apply K-Modes clustering
set.seed(123)
k <- 23  # Number of clusters
kmodes_result <- kmodes(features, modes = k)

# Add cluster information to the data
new_data$Cluster <- kmodes_result$cluster




```



```{r}
#Function to find similar animations within each cluster without checking for similar words

find_similar_animations <- function(animation_name, cluster_data) {
  similar_animations <- cluster_data$Name[cluster_data$Name != animation_name]
  
  if (length(similar_animations) > 12) {
    similar_animations <- similar_animations[1:12]
  } else if (length(similar_animations) < 12) {
    similar_animations <- c(similar_animations, rep(NA, 12 - length(similar_animations)))
  }
  
  return(similar_animations)
}

# Process for each animation in the list
results <- list()

for (i in 1:nrow(new_data)) {
  animation_name <- new_data$Name[i]
  cluster_id <- new_data$Cluster[i]
  cluster_data <- new_data[new_data$Cluster == cluster_id, ]
  similar_animations <- find_similar_animations(animation_name, cluster_data)
  results[[animation_name]] <- similar_animations
}

# Convert the results list to a dataframe
results_df <- do.call(rbind, lapply(names(results), function(x) {
  cbind(Animation = x, setNames(as.data.frame(t(results[[x]])), paste0("Similar_", 1:12)))
}))
desktop_path <- file.path(Sys.getenv("USERPROFILE"), "Desktop", "Similar_K-Modes")

# Save the data to a CSV file on the desktop
write_csv(results_df, desktop_path)

# Display confirmation message
print("The data has been successfully saved to a CSV file on the desktop.")
```

K-Prototypes

```{r}
#  load clustMixType library
library(clustMixType)

# Assume data contains your data
# Select numeric and categorical columns
numeric_columns <- c("IMDB_Link", "Amtiaz", "Number_People") # Replace with the names of numeric columns
categorical_columns <- c("Series", "Animation", "Western", "Adventure", "Comedy", "Family", "Fantasy", "Mystery", "Action", "Romance", "Drama", "SciFi", "ShortFilm", "Crime", "Musical", "Korean", "Thriller", "Anime", "Music") # Replace with the names of categorical columns
# Convert categorical variables to factors
data[categorical_columns] <- lapply(data[categorical_columns], as.factor)

# Check that categorical variables have been converted to factors
str(data[categorical_columns])
# Perform K-Prototypes
set.seed(123)
k <- 12  # Number of clusters
kproto_result <- kproto(data[, c(numeric_columns, categorical_columns)], k = k)

# Add cluster information to the data
data$Cluster <- kproto_result$cluster

# Display results
print(data)


```

```{r}


# Process for each animation in the list
results <- list()

for (i in 1:nrow(data)) {
  animation_name <- data$Name[i]
  cluster_id <- data$Cluster[i]
  cluster_data <- data[data$Cluster == cluster_id, ]
  similar_animations <- find_similar_animations(animation_name, cluster_data)
  results[[animation_name]] <- similar_animations
}

#  Convert the results list to a dataframe
results_df <- do.call(rbind, lapply(names(results), function(x) {
  cbind(Animation = x, setNames(as.data.frame(t(results[[x]])), paste0("Similar_", 1:12)))
}))
desktop_path <- file.path(Sys.getenv("USERPROFILE"), "Desktop", "Similar_K-Prototypes")

# Save the data to a CSV file on the desktop
write_csv(results_df, desktop_path)

# Display confirmation message
print("The data has been successfully saved to a CSV file on the desktop.")

```

Gower’s Dissimilarity , PAM

```{r}
library(cluster)
new2_data <- data[, c("Series", "Animation", "Western", "Adventure", "Comedy", "Family", "Fantasy", "Mystery", "Action", "Romance", "Drama", "SciFi", "ShortFilm", "Crime", "Musical", "Korean", "Thriller", "Anime", "Music","IMDB_Link", "Amtiaz", "Number_People")]

# Assume data contains your data
# Compute Gower dissimilarity index
gower_dist <- daisy(new2_data, metric = "gower")

# Run PAM algorithm
set.seed(123)
k <- 30  # Number of clusters
pam_result <- pam(gower_dist, k = k)

# Add cluster information to the data
new2_data$Cluster <- pam_result$clustering
new2_data$Name <- data$Name

# Display results
print(new2_data)


```


```{r}


# Process for each animation in the list
results <- list()

for (i in 1:nrow(new2_data)) {
  animation_name <- new2_data$Name[i]
  cluster_id <- new2_data$Cluster[i]
  cluster_data <- new2_data[new2_data$Cluster == cluster_id, ]
  similar_animations <- find_similar_animations(animation_name, cluster_data)
  results[[animation_name]] <- similar_animations
}

# Convert the results list to a dataframe
results_df <- do.call(rbind, lapply(names(results), function(x) {
  cbind(Animation = x, setNames(as.data.frame(t(results[[x]])), paste0("Similar_", 1:12)))
}))

desktop_path <- file.path(Sys.getenv("USERPROFILE"), "Desktop", "similar_pam.csv")

# Save the data to a CSV file on the desktop
write_csv(results_df, desktop_path)

# Display confirmation message
print("The data has been successfully saved to a CSV file on the desktop.")
```

K-Means

```{r}
# Load required libraries
library(dplyr)
library(cluster)

# Assume new3_data contains your data
new3_data <- data[, c("IMDB_Link", "Amtiaz", "Number_People")]

# Standardize the numeric columns (optional but recommended)
new3_data_scaled <- scale(new3_data)

# Determine the number of clusters (K) using the Elbow method (optional)
wss <- (nrow(new3_data_scaled) - 1) * sum(apply(new3_data_scaled, 2, var))
for (i in 2:15) {
  wss[i] <- sum(kmeans(new3_data_scaled, centers = i)$tot.withinss)
}
plot(1:15, wss, type = "b", xlab = "Number of Clusters", ylab = "Within groups sum of squares")

# Set the number of clusters (K) based on the Elbow method or desired value
k <- 5  # You can change this value based on the Elbow plot or desired number of clusters

# Apply K-Means clustering
set.seed(123)
kmeans_result <- kmeans(new3_data_scaled, centers = k, nstart = 25)

# Add cluster information to the data
new3_data$Cluster <- kmeans_result$cluster
new3_data$Name <- data$Name  # Adding Name column for reference

# Display results
print(new3_data)

```

```{r}

# Process for each animation in the list
results <- list()

for (i in 1:nrow(new3_data)) {
  animation_name <- new3_data$Name[i]
  cluster_id <- new3_data$Cluster[i]
  cluster_data <- new3_data[new3_data$Cluster == cluster_id, ]
  similar_animations <- find_similar_animations(animation_name, cluster_data)
  results[[animation_name]] <- similar_animations
}

# Convert the results list to a dataframe
results_df <- do.call(rbind, lapply(names(results), function(x) {
  cbind(Animation = x, setNames(as.data.frame(t(results[[x]])), paste0("Similar_", 1:12)))
}))
desktop_path <- file.path(Sys.getenv("USERPROFILE"), "Desktop", "similar_K-Means.csv")

# Save the data to a CSV file on the desktop
write_csv(results_df, desktop_path)

# Display confirmation message
print("The data has been successfully saved to a CSV file on the desktop.")
```


These selections were made based on the clustering method we used

My approach:

Now, if we want to create a list of similar animations for recommendation on a website, we need to use clustering.

In this method, I first select animations with common words as part of similar animations.

Then, using K-Prototypes, I select similar animations that do not have common words.

```{r}
library(dplyr)
library(stringr)
library(readr)
library(clustMixType)

# Assume we have a list of animation names
animation_names <- data$Name

# Function to preprocess names
preprocess_name <- function(name) {
  words <- str_split(tolower(name), "\\W+")[[1]]
  words <- words[words != "انیمیشن" & nchar(words) > 2]
  return(words)
}

# Extract words
animation_words <- lapply(animation_names, preprocess_name)

# Find similar animations
similar_animations <- lapply(seq_along(animation_words), function(i) {
  similar <- sapply(seq_along(animation_words), function(j) {
    if (i != j && any(animation_words[[i]] %in% animation_words[[j]])) {
      return(animation_names[j])
    } else {
      return(NA)
    }
  })
  similar <- similar[!is.na(similar)]
  if (length(similar) < 12) {
    similar <- c(similar, rep("#", 12 - length(similar)))
  } else {
    similar <- similar[1:12]
  }
  return(similar)
})

# Create data frame and save to CSV file
df <- data.frame(Animation_Name = animation_names, do.call(rbind, similar_animations))
colnames(df)[2:13] <- paste0("Similar_", 1:12)
numeric_columns <- c("IMDB_Link", "Amtiaz", "Number_People")
categorical_columns <- c("Series", "Animation", "Western", "Adventure", "Comedy", "Family", "Fantasy", "Mystery", "Action", "Romance", "Drama", "SciFi", "ShortFilm", "Crime", "Musical", "Korean", "Thriller", "Anime", "Music")
data[categorical_columns] <- lapply(data[categorical_columns], as.factor)
set.seed(123)
k <- 12
kproto_result <- kproto(data[, c(numeric_columns, categorical_columns)], k = k)
data$Cluster <- kproto_result$cluster

# Fill in missing values based on the cluster
df <- df %>%
  rowwise() %>%
  mutate(across(starts_with("Similar_"), ~ ifelse(. == "#", 
                sample(animation_names[data$Cluster == data$Cluster[which(animation_names == Animation_Name)]], 1), .)))
desktop_path <- file.path(Sys.getenv("USERPROFILE"), "Desktop", "similar_animations.csv")

# Save the data to a CSV file on the desktop
write_csv(df, desktop_path)

# Display confirmation message
print("The data has been successfully saved to a CSV file on the desktop.")


```

But there is still an error; for instance, the word 'dog' has two letters. To reduce this error, we do not remove all two-letter words, but rather those that are redundant

First, identify redundant two- and three-letter words.

```{r}
library(tidyverse)

animation_names <- data$Name

# Function to preprocess names
preprocess_name <- function(name) {
  words <- str_split(tolower(name), "\\W+")[[1]]
  words <- words[words != "انیمیشن"]
  return(words)
}

# Extract words from animation names
words_list <- unlist(map(animation_names, preprocess_name))

# Filter two-letter and three-letter words
short_words <- words_list[nchar(words_list) == 2 | nchar(words_list) == 3]

# Remove duplicate words
unique_short_words <- unique(short_words)

# Print the unique two-letter and three-letter words
print(unique_short_words)

```


```{r}
library(dplyr)
library(stringr)
library(readr)
library(clustMixType)

# Assume we have a list of animation names
animation_names <- data$Name

# List of harof_izafeh
harof_izafeh <- c("ها", "حال", "یا", "یه", "پن", "چه", "اگر", "دهد", "آور", "هی", "شدن", "اوه")

# Function to preprocess names and remove harof_izafeh
preprocess_name <- function(name) {
  words <- str_split(tolower(name), "\\W+")[[1]]
  words <- words[words != "انیمیشن" & nchar(words) > 1]
  words <- words[!words %in% harof_izafeh]
  return(words)
}

# Extract words
animation_words <- lapply(animation_names, preprocess_name)

# Find similar animations
similar_animations <- lapply(seq_along(animation_words), function(i) {
  similar <- sapply(seq_along(animation_words), function(j) {
    if (i != j && any(animation_words[[i]] %in% animation_words[[j]])) {
      return(animation_names[j])
    } else {
      return(NA)
    }
  })
  similar <- similar[!is.na(similar)]
  if (length(similar) < 12) {
    similar <- c(similar, rep("#", 12 - length(similar)))
  } else {
    similar <- similar[1:12]
  }
  return(similar)
})

# Create data frame and save to CSV file
df <- data.frame(Animation_Name = animation_names, do.call(rbind, similar_animations))
colnames(df)[2:13] <- paste0("Similar_", 1:12)
numeric_columns <- c("IMDB_Link", "Amtiaz", "Number_People")
categorical_columns <- c("Series", "Animation", "Western", "Adventure", "Comedy", "Family", "Fantasy", "Mystery", "Action", "Romance", "Drama", "SciFi", "ShortFilm", "Crime", "Musical", "Korean", "Thriller", "Anime", "Music")
data[categorical_columns] <- lapply(data[categorical_columns], as.factor)
set.seed(123)
k <- 12
kproto_result <- kproto(data[, c(numeric_columns, categorical_columns)], k = k)
data$Cluster <- kproto_result$cluster

# Fill in missing values based on the cluster
df <- df %>%
  rowwise() %>%
  mutate(across(starts_with("Similar_"), ~ ifelse(. == "#", 
                sample(animation_names[data$Cluster == data$Cluster[which(animation_names == Animation_Name)]], 1), .)))
desktop_path <- file.path(Sys.getenv("USERPROFILE"), "Desktop", "similar_animations2.csv")

# Save the data to a CSV file on the desktop
write_csv(df, desktop_path)

# Display confirmation message
print("The data has been successfully saved to a CSV file on the desktop.")

```

In my opinion, this list is the best recommendation for introducing twelve different animations.
